SPIN Novelty Data

### 2019-11-26 stats/kids_basic_me.Rmd

```{r setup}
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(brms)
library(here)
library(brmstools)
library(ggpubr)
library(rwebppl)
```

@@

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
          age_month = lubridate::time_length(difftime(test_date,dob), "month"),
         age_month = round(age_month),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
  filter(trial != "train1",
           trial != "train2")%>%
  mutate(item = familiar,
         age = age_num - min(age_num))%>%
  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiar, -rt)

>>>>

```{r setup}
library(tidyverse)
library(knitr)
library(langcog)
library(ggthemes)
library(jsonlite)
library(readxl)
library(brms)
library(here)
#library(brmstools)
library(ggpubr)
library(rwebppl)
```

@@

d <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         age_num_month = lubridate::time_length(difftime(test_date,dob), "month"),
         age_num_month = round(age_num_month)/12,
         age_month = age_num_month - min(age_num_month),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F))%>%
  filter(trial != "train1",
           trial != "train2")%>%
  mutate(item = familiar,
         age = age_num - min(age_num))%>%
  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -familiar, -rt)

### 2019-11-26 stats/kids_familiar_words.Rmd
update fam picture plot

d_select <- d %>%
  mutate(select = if_else(d$Word %in% select, 1.5,-1),
         image = paste("../experiments/kids/images/",Word,".png", sep=""))
```

@@

>>>>

d_select <- d %>%
  mutate(select = if_else(d$Word %in% spin_select, 1.5,-1),
         image = paste("../experiments/kids/images/",Word,".png", sep=""))
```

@@

```{r}
ggsave("../graphs/talk_items_selection.pdf", width = 12, height = 8, scale = 1.5)
```

### 2019-11-26 stats/kids_novelty.Rmd

d_spin <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep",
         trial != "train1", trial != "train2")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         age_num_month = lubridate::time_length(difftime(test_date,dob), "month"),
         age_num_month = round(age_num_month),
         age_month = age_num_month - min(age_num_month),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         experiment = condition)%>%
  mutate(age = age_num - min(age_num))%>%
  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -rt)
# 
# 
# ## import mcc data
# 
# files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round2/")
# 
# raw_data_mcc <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round2/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,51,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
#   raw_data_mcc <- bind_rows(raw_data_mcc, id)
# }
# 
# d_raw_mcc <-raw_data_mcc %>%
#   mutate(subage = ifelse(subid =="180810_14_nov","2",subage),
#          test_date = as.Date(test_date))
# 
# 
# log_mcc <- read_excel("~/Work/MCC/git-mcc/MCC-subject_log.xlsx", 1)%>%
#   filter(Condition == "nov")%>%
#   mutate(dob = as.numeric(dob),
#          dob = as.Date(dob,origin = "1899-12-30"))%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
# 
# d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
#   filter(keep_drop == "keep")%>%
#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
#          leftObject = leftFruit,
#          rightObject = rightFruit,
#          pick = str_sub(pick,72,str_length(pick)-4),
#          agent = ifelse(speakerChange == "false", agent,altAgent),
#          experiment = "dis_novelty_mcc")%>%
#   filter(speakerChange == "false", trial != "train")%>%
#   select(-speakerChange,-altAgent,-leftFruit,-rightFruit)
# 
# 
# # join datasets
# 
# d <- bind_rows(d_spin, d_mcc)
# 
write_csv(d_spin, "../data/novelty.csv")

>>>>

d_spin <- left_join(d_raw,log, by = "subid")%>%
  filter(keep_drop == "keep",
         trial != "train1", trial != "train2")%>%
  mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
         age_num_month = lubridate::time_length(difftime(test_date,dob), "month"),
         age_num_month = round(age_num_month)/12,
         age_month = age_num_month - min(age_num_month),
         check_age = ifelse(substr(age_num,1,1) == subage, T, F),
         experiment = condition)%>%
  mutate(age = age_num - min(age_num))%>%
  select(-pick_src, -test_date, -experimenter, - keep_drop, -dob, -sex, -check_age, - condition, -rt)
# 
# 
# ## import mcc data
# 
# files <- dir("~/Work/MCC/git-mcc/kids_novel_data/round2/")
# 
# raw_data_mcc <- data_frame()
# for (f in files) {
#   jf <- paste("~/Work/MCC/git-mcc/kids_novel_data/round2/",f,sep="")
#   jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
#   date <- str_sub(jf,51,str_length(jf)-11)
#   id <- as_data_frame(jd$data$data) %>% mutate(test_date = date)
#   raw_data_mcc <- bind_rows(raw_data_mcc, id)
# }
# 
# d_raw_mcc <-raw_data_mcc %>%
#   mutate(subage = ifelse(subid =="180810_14_nov","2",subage),
#          test_date = as.Date(test_date))
# 
# 
# log_mcc <- read_excel("~/Work/MCC/git-mcc/MCC-subject_log.xlsx", 1)%>%
#   filter(Condition == "nov")%>%
#   mutate(dob = as.numeric(dob),
#          dob = as.Date(dob,origin = "1899-12-30"))%>%
#   select(subid,experimenter,keep_drop,sex,dob)
# 
# 
# d_mcc <- left_join(d_raw_mcc,log_mcc, by = "subid")%>%
#   filter(keep_drop == "keep")%>%
#   mutate(age_num = lubridate::time_length(difftime(test_date,dob), "years"),
#          check_age = ifelse(substr(age_num,1,1) == subage, T, F),
#          leftObject = leftFruit,
#          rightObject = rightFruit,
#          pick = str_sub(pick,72,str_length(pick)-4),
#          agent = ifelse(speakerChange == "false", agent,altAgent),
#          experiment = "dis_novelty_mcc")%>%
#   filter(speakerChange == "false", trial != "train")%>%
#   select(-speakerChange,-altAgent,-leftFruit,-rightFruit)
# 
# 
# # join datasets
# 
# d <- bind_rows(d_spin, d_mcc)
# 
write_csv(d_spin, "../data/novelty.csv")
